### 2022-11-04 inst/Examples/Paper_results/Paper_results_2.Rmd
Added support for general Gaussian noise models
Added support for custom Gaussian models for the noise component to be added using rgeneric. Added functions to make this specification easier, and made changes to plot, summary, etc such that the results can interpret the results from the new model property

>>>>

ggd = data.frame(age=data$age,depth=data$depth,proxy=data$proxy)
ggdr = data.frame(depths=events_rasmussen$depth[events_rasmussen$depth>1492.45 & events_rasmussen$depth<2426],ages=events_rasmussen$age[events_rasmussen$age>11703.07 & events_rasmussen$age < 59944.50])
library(ggplot2)
ggp2 = ggplot(data=ggd) + theme_bw()+
  geom_line(aes(x=age,y=proxy),col="black",size=0.5)+
  geom_vline(data=ggdr,mapping=aes(xintercept=ages),col="gray",size=0.5)+
  xlab("GICC05 age (yb2k)") + ylab(expression(paste(delta^18,"O (permil)")))

# ggsave("proxyplot-bw-4800x2000.eps", device=cairo_ps,width=4800,height=2000,units="px",dpi=500,limitsize=FALSE)

# ggplot(data=ggd)+geom_line(aes(x=depth,y=age))
